---
title: "penguin_assignment_github"
Purpose of this script: "Load and clean penguin data, run a statistical test on it before plotting and saving a figure of the data"
output: html_document
date: "`r Sys.Date()`"
---

set the working directory -- where R will look for files and folders. 
setwd()

Loading the data
```{r}
#load the necessary packages from my file
source("functions/libraries.r")

#load functions from my files
source("functions/clean_columns.r")
source("functions/plotting.r")

#load the raw penguin data
penguins_raw <- read.csv("data_raw/penguins_raw.csv")

```

Cleaning the data
```{r}
#call the cleaning function we created to clean our raw penguin data by fixing column names, removing empty rows (NA) and removing "comment" and "delta" columns
penguins_clean <- clean_columns(penguins_raw)
names(penguins_clean)

#save the clean data into our data_clean folder within the directory
write.csv(penguins_clean,"data_clean/penguins_clean.csv")

```

Removing NAs from the clean data
```{r}
#call the function that removes rows containing NAs from the culmen_length and body_mass-g columns and subsets this data
penguins_NA <- remove_NA(penguins_clean)
head(penguins_NA)

```

Running a statistical test
```{r}
#Linear regression model looking at the relationship between CULMENLENGTH and BODYMASS [Does body mass affect culmen length?]

#check if the variables correctly are non-categorical (output should = FALSE)
is.factor(penguins_clean$culmen_length_mm) #FALSE
is.factor(penguins_clean$body_mass_g) #FALSE

#use a simple regression model to test this relationship
penguin_lm <- lm(culmen_length_mm ~ body_mass_g, data = penguins_clean)

#check results of the linear model
summary(penguin_lm) 

```
p value = <2e-16, which is significantly lower than 0.05; therefore, there is a statistically significant positive association between body mass and culmen length in these penguin species


Create a scatter plot visualising this linear regression model
```{r}
#call in the plotting function to create a plot visualising this linear regression model
lm_graph <- plot_length_mass(penguins_NA)
lm_graph

```

Save the figure as a vector image
```{r}
#call in a function to save the current figure as a vector image in the figures folder within our directory
save_lm_plot_svg(penguins_NA, 
                      "figures/lm_vector.svg", 
                      size = 15, scaling = 1)
```



